### 2008-12-20 talk/ecoop2009/intro.tex
fix few XXXs

Most JIT compilers for dynamic languages around (such as IronPython, Jython,
JRuby \anto{XXX insert some reference}) compile code at the method
granularity.  If on the one hand they can exploit some of the knowledge gathered
at runtime (e.g. the types of method parameters), on the other hand they can
do little to optimize most of the operations inside, because their behaviour
depends on informations that are not available at compile-time, because
e.g. the global state of the program can change at runtime. \anto{e.g., we can
  add/remove methods to classes, etc. Should we insert some example here?}
\cfbolz{the last sentence is waaay too complicated}

>>>>

Most JIT compilers for dynamic languages around (such as
IronPython \footnote{http://www.codeplex.com/IronPython},
Jython \footnote{http://www.jython.org/} or
JRuby \footnote{http://jruby.codehaus.org/}) compile code at the method
granularity.  If on the one hand they can exploit some of the knowledge
gathered at runtime (e.g. the types of method parameters), on the other hand
they can do little to optimize most of the operations inside, because few
assumptions can be made about the global state of the program.
